Add a README

### 2024-09-07 add_readme.qmd
Fix typo and format raw output nicely

    An overview over the system dependencies of one more multiple R packages can be created using the function `pkg_sysreqs()` from the R package `pak`. In combination with `renv`, we can obtain the system dependencies of all R packages in the current project:

@@

    ```
    ── Install scripts ─────────────────────── 
    dnf install -y make pandoc

@@

    ```
    [✓] Checking tools....................OK
          TinyTeX: (not installed)
          Chromium: (not installed)

>>>>

    An overview over the system dependencies of R packages can be created using the function `pak::pkg_sysreqs()`. In combination with `renv`, we can obtain the system dependencies of all R packages in the current project:

@@

    ```txt
    ── Install scripts ─────────────────────── 
    dnf install -y make pandoc

@@

    ```txt
    [✓] Checking tools....................OK
          TinyTeX: (not installed)
          Chromium: (not installed)
